Measuring Political Freedom Around the World

### 2020-11-12 slides.Rmd
updated slides

--
* From Data provided by the Gapminder Foundation.

@@

* summarsze fh index

@@

# Best Subsets
```{r message=FALSE}
subsets %>% 
  group_by(df) %>% 
  filter(adj.r.squared == max(adj.r.squared)) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  rename(a_rsq = adj.r.squared) %>% 
  select(df, a_rsq, model) %>% 
  arrange(desc(a_rsq)) %>% 
DT::datatable(fillContainer = FALSE, options = list(pageLength = 3))
```

@@

class: center

```{r, message=FALSE, warning=FALSE}
r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))

subsets %>% 
  ggplot(aes(x = df, y = adj.r.squared)) + 
  geom_point() + 
  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "Green") + 
  labs(title = "", x = "Parameters", y = "Adjusted R Squared") + 
  scale_x_continuous(breaks = 1:9) + 
  theme_light(base_size = 30)
```

@@

# Model
---

@@

```{r}
broom::tidy(model_df5) %>% 
  kable()
```
---
class: center
$$
\small
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(model_df5) %>% 
  kable() %>% 
  row_spec(4, bold = T, color = "white", background = "#D7261E")
```

>>>>

* From Data provided by the Gapminder Foundation.

@@

* summarsze fh index
https://docs.google.com/spreadsheets/d/1AmmTVOAFMXZx3a-OYyKQaNM-dQJAvGCJOwfWzixo2Pk/edit#gid=266682269

@@

# Best Subsets by Adjusted R Squared
```{r message=FALSE}
subsets %>% 
  group_by(df) %>% 
  filter(adj.r.squared == max(adj.r.squared)) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  rename(a_rsq = adj.r.squared) %>% 
  select(df, a_rsq, model) %>% 
  arrange(desc(a_rsq)) %>% 
DT::datatable(fillContainer = FALSE, options = list(pageLength = 3), 
              colnames = c("DF", "A_Rsq", "Model"))
```

---
# Best Subsets by AIC
```{r message=FALSE}
subsets %>% 
  group_by(df) %>% 
  filter(AIC == min(AIC)) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  select(df, AIC, model) %>% 
  arrange(AIC) %>% 
DT::datatable(fillContainer = FALSE, options = list(pageLength = 3),
              colnames = c("DF", "AIC", "Model"))
```

@@

# Best Subsets by BIC
```{r message=FALSE}
subsets %>% 
  group_by(df) %>% 
  filter(BIC == min(BIC)) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  select(df, BIC, model) %>% 
  arrange(BIC) %>% 
DT::datatable(fillContainer = FALSE, options = list(pageLength = 3),
              colnames = c("DF", "BIC", "Model"))
```

# Best Subsets

```{r, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))

subsets %>% 
  ggplot(aes(x = df, y = adj.r.squared)) + 
  geom_point() + 
  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "Green") + 
  labs(title = "", x = "Parameters", y = "Adjusted R Squared") + 
  scale_x_continuous(breaks = 1:9) + 
  theme_test(base_size = 30)
```

# Best Subsets

```{r, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
r <- subsets %>% group_by(df) %>% summarise(AIC = max(AIC, na.rm = T))

subsets %>% 
  ggplot(aes(x = df, y = AIC)) + 
  geom_point() + 
  geom_smooth(data = r, aes(df, AIC), se = FALSE, span = 0.5, color = "red") + 
  labs(title = "", x = "Parameters", y = "AIC") + 
  scale_x_continuous(breaks = 1:9) + 
  theme_test(base_size = 30)
```

@@

# Model

@@

```{r}
broom::tidy(model_df5) %>% 
  kable()
```

***
```{r}
broom::glance(model_df5) %>% 
  select(r.squared, adj.r.squared, adj.r.squared, AIC, BIC) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  kable()
```

---
class: center
$$
\small
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(model_df5) %>% 
  kable() %>% 
  row_spec(2, color = "white", background = "#D7261E")
```

***

```{r}
broom::glance(model_df5) %>% 
  select(r.squared, adj.r.squared, adj.r.squared, AIC, BIC) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  kable()
```

---
class: center
$$
\small
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(model_df5) %>% 
  kable() %>% 
  row_spec(3, color = "white", background = "#D7261E")
```

***

```{r}
broom::glance(model_df5) %>% 
  select(r.squared, adj.r.squared, adj.r.squared, AIC, BIC) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  kable()
```

---
class: center
$$
\small
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(model_df5) %>% 
  kable() %>% 
  row_spec(4, color = "white", background = "#D7261E")
```

***

```{r}
broom::glance(model_df5) %>% 
  select(r.squared, adj.r.squared, adj.r.squared, AIC, BIC) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  kable()
```

class: center
$$
\small
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(model_df5) %>% 
  kable() %>% 
  row_spec(5, color = "white", background = "#D7261E")
```

***

```{r}
broom::glance(model_df5) %>% 
  select(r.squared, adj.r.squared, adj.r.squared, AIC, BIC) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  kable()
```

---
class: center
$$
\small
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(model_df5) %>% 
  kable() %>% 
  row_spec(6, color = "white", background = "#D7261E")
```

***

```{r}
broom::glance(model_df5) %>% 
  select(r.squared, adj.r.squared, adj.r.squared, AIC, BIC) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  kable()
```
